si: code and prose exploring Spatial Interaction models

### 2022-04-22 README.qmd
Update with nse the same as se

What just happened?
We created an 'OD data frame' from geographic origins and destinations, and then estimated a simple gravity model based on the population in origin and destination zones and a custom distance decay function.
As the example above shows, the package allows/encourages you to define and use your own functions to estimate the amount of interaction/movement between places.

Note: this approach also allows you to use {si} functions in {dplyr} pipelines:

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               beta = 0.3)
od_res %>% 
  select(interaction)
```

>>>>

What just happened?
We created an 'OD data frame' with the function `si_to_od()` from geographic origins and destinations, and then estimated a simple 'production constrained' (with the `constraint_p` argument) gravity model based on the population in origin and destination zones and a custom distance decay function with `si_calculate()`.
As the example above shows, the package allows/encourages you to define and use your own functions to estimate the amount of interaction/movement between places.

The approach is also 'tidy', allowing use of {si} functions in {dplyr} pipelines:

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               constraint_p = origin_all,
               beta = 0.3)
od_res %>% 
  select(interaction)
```
